Scalable and Parameter-Free Exploration in Deep Reinforcement Learning

### 2022-01-12 papers/main.tex
TEMPORARY DEPLOY COMMIT

\begin{itemize}
    \item Near-optimal regret
    \item Incorporate domain knowledge
    \item Avoid hyperparameter optimization
\end{itemize}

@@

We would like to approximate the posterior distribution of the Q-value function.
This would (1) give near-optimal regret, (2) let us incorporate domain knowledge
through an appropriate prior distribution.
We can use the functional variational bayesian neural
network (FVBNN)~\citep{sun_functional_2019} framework discussed earlier.
NoisyNet uses one sample from Q for each optimization step. We will instead use
\(N\) samples
from Q. This lets us add the KL-term from FVBNN to the loss function that
encourages stochasticity.
The maximization target becomes:
\begin{equation}
    \log p(\D_\omega^N \vert f) - \KL \left[ q(\f^{\D_\omega^N}, \f^M) \Vert p(\f^{\D_\omega^N}, \f^M) \right],
\end{equation}
where \(\f^{\D_\omega^N}\) is \(f\) applied to the dataset \(\D_\omega^N\), and \(\f^M\) is \(f\) applied to
a set of i.i.d. random points \(M = \{m_i \sim c \mid i=1,\dots,k\} \subseteq \state \times \action\)
with full support. We will let

\begin{equation}
    M = \{(s_i, a_j) \; \forall s_i \in \D_\omega^N,\, \forall a_j \in \action\}. 
\end{equation}
%To justify this we need to show that \(supp(c) = \state \times \action\).
%Under the same assumption about the distribution of each state \(s_i\) from BBO,
%\(supp(c) = \state \times \action\) follows trivially.

Since we are modeling \(q_\phi\) with a Bayesian neural network, and \(Q_\omega\) with a neural network,
we have a bilevel optimization problem. To solve this, we employ a similar strategy to \citet{fellows_bayesian_2021},
where we have a two-timescale gradient update. \(\phi\) and \(\omega\) are updated using stochastic
gradient descent at different timescales to ensure stable convergence.

@@

\section{Experiments}
Since our method is essentially an extension of NoisyNet~\cite{fortunato_noisy_2019}, all experiments will compare the performance results of these two methods.
\subsection{Uninformative Prior}
First, it is interesting to see how our method will compare in environments without the advantage of prior knowledge. We hypothesize that the added KL-term will push the algorithm to keep exploring more than NoisyNet, and

@@

\subsection{Informative Prior}
We will also look at how our method can utilize domain knowledge to improve sample efficiency. We will use the following method to calculate the prior distribution on the Q-values:

\textcolor{red}{Discuss how to go from policy prior to Q-value prior.}

@@

>>>>

\begin{itemize}
    \item Efficient exploration
    \item Incorporate domain knowledge
    \item Avoid hyperparameter optimization
\end{itemize}

@@

We would like to approximate the posterior distribution of the Q-value function.
\citet{osband_why_2017} proove that in finite horizon MDPs posterior sampling for
reinforcement learning has at least a near-optimal regret bound. They further conjecture
that this cound can be further improved to show an optimal regret bound. Additionally,
a posterior sampling based reinfrocement learning algorithm could be made to utilize
prior information or domain knowledge through an appropriate prior. This should improve
policy convergence rate.
Combined with the computational efficiency of posterior sampling, this motivates the
development of a Bayesian reinforcement learning algorithm with functional priors.

We can use the functional variational bayesian neural
network (FVBNN)~\citep{sun_functional_2019} framework discussed earlier.
NoisyNet uses one sample from Q for each optimization step. We will instead use
\(N\) samples from Q. This lets us add the KL-term from FVBNN to the loss function that
encourages stochasticity.
The maximization target becomes:
\begin{equation}
    \log p(\D_\omega^N \vert f) - \KL \left[ q(\f^{\D_\omega^N}, \f^\mathbf{M}) \Vert p(\f^{\D_\omega^N}, \f^\mathbf{M}) \right],
\end{equation}
where \(\f^{\D_\omega^N}\) is \(f\) applied to the dataset \(\D_\omega^N\), and \(\f^\mathbf{M}\) is \(f\) applied to
a set of i.i.d. random points \(\mathbf{M} = \{m_i \sim c \mid i=1,\dots,k\} \subseteq \state \times \action\)
with full support. We will let the measurement \(\mathbf{M}\) be the the set of all state-action
pairs for states we have already explored. If the MDP is ergodic, then \(\textbf{M}\) will eventually
have full support in \(\state \times \action\).

\begin{equation}
    \mathbf{M} = \{(s_i, a_j) \; \forall s_i \in \D_\omega^N,\, \forall a_j \in \action\}. 
\end{equation}

%To justify this we need to show that \(supp(c) = \state \times \action\).
%Under the same assumption about the distribution of each state \(s_i\) from BBO,
%\(supp(c) = \state \times \action\) follows trivially.

% Since we are modeling \(q_\phi\) with a Bayesian neural network, and \(Q_\omega\) with a neural network,
% we have a bilevel optimization problem. To solve this, we employ a similar strategy to \citet{fellows_bayesian_2021},
% where we have a two-timescale gradient update. \(\phi\) and \(\omega\) are updated using stochastic
% gradient descent at different timescales to ensure stable convergence.

@@

\section{Experiments}
Our method most closely resembles that of NoisyNet~\cite{fortunato_noisy_2019}, so
all experiments will mainly compare the performance of these two methods.
\subsection{Uninformative Prior}
First, it is interesting to see how our method will compare to NoisyNet
in environments without the advantage of prior knowledge.
We hypothesize that the added KL-term will push the algorithm to keep exploring unexplored
state-action pairs more than NoisyNet, thus

@@

\subsection{Informative Prior}
One of the benefits of a functional prior is that we can incorporate domain knowledge to
get more efficient exploration. We will now look at how our method can utilize domain
knowledge to improve sample efficiency.

% We will use the following method to calculate the prior distribution on the Q-values:

% \textcolor{red}{Discuss how to go from policy prior to Q-value prior.}

@@

\section{Conclusion}
